Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
revised description of two-stage verifier

The second approach is illustrated in Fig.~\ref{fig:CEGIS} and 
uses a two-stage verification with a first stage that performs unsound fixed point operations given the precision \param{I_b}{F_b}, and a second stage that restores soundness by validating these operations using interval arithmetic on the synthesised plant.

>>>>

The second approach is illustrated in Fig.~\ref{fig:CEGIS} and uses a
two-stage verification: the first stage performs potentially unsound
fixed-point operations assuming a precision \param{I_b}{F_b}, and the
second stage restores soundness by validating these operations
using interval arithmetic on the synthesised controller.
